Poker Chips, Earthquakes, and Computation

### 2014-10-13 finaldraft.tex

Our goal in introducing this more complicated model of computation is to allow ourselves to build a board that can compute NOT. The following board does so:
\begin{figure}
\centering
\includegraphics[width=0.5\linewidth]{notgate}
\caption{Board which computes $f(x) = \neg x$}
\label{fig:NOT}
\end{figure}
We note that in Figure~\ref{fig:NOT}, the number of nodes between the 4 and $r$ is same as the number of nodes between the 4 and the output node, but the number of nodes separating the input node and $r$ is shorter than the number of nodes separating the 4 and the output node. If $i$ is set to $1$, then $r$ will be activated while the output only has 3 chips on it, so the output will be read as 0. If the input is set to 0, then $r$ and the square adjacent to $o$ will both have 4 chips on them at same time so the output will be $1$. This computes $f(x) = \neg x$. However, we have switched the standard positions of $r$ and the output node, so it is unclear how to compose this board with other ones. 
\end{document}

>>>>

Our goal in introducing this more complicated model of computation is to allow ourselves to build a board that can compute NOT. The following board does so:
\begin{figure}
\centering
\includegraphics[width=0.5\linewidth]{notgate}
\caption{Board which computes $f(x) = \neg x$}
\label{fig:NOT}
\end{figure}

We note that in Figure~\ref{fig:NOT}, the number of nodes between the 4 and $r$ is same as the number of nodes between the 4 and the output node, but the number of nodes separating the input node and $r$ is shorter than the number of nodes separating the 4 and the output node. If $i$ is set to $1$, then $r$ will be activated while the output only has 3 chips on it, so the output will be read as 0. If the input is set to 0, then $r$ and the square adjacent to $o$ will both have 4 chips on them at same time so the output will be $1$. This computes $f(x) = \neg x$. However, we have switched the standard positions of $r$ and the output node, so it is unclear how to compose this board with other ones.

\section{Poem}

\begin{quote}
A board with chips.\\
An earthquake redistibutes some chips.\\
New board! never turn back. \\ \\

Another earthquake hits.\\
And another earthquakes hits again.\\
Who cares which first! \\ \\

One last earthquake\\
So many it must be Japan.\\
Computation.
\end{quote}
\end{document}
